---
title: "WUP-3"
author: "Yessica Garay"
date: "2024-02-14"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tigerstats)
library(tidyverse)
davisdata=read.csv('UCDavis.csv')
```

# Introduction
The research question is this: is there a diffrence in the average amount of alcohol consumed per week by students who sit in row 1, row 2 or row3 the UCdavis classroom


$H_0$: There is no difference between the average number of drinks imbibed between people based on the row they sit in.

$H_A$: The average number drinks is different between at least two rows.


# Methods

Data from UC Davis: Seat is categorical, and alcohol is numerical, so we used the Numerical~Cat helper file

# Description 
## graphical description


```{r}
boxplot(alcohol~Seat,data=davisdata)
```

This boxplot shows that students who sit in the back row tend to drink more

## numerical description


```{r}
favstats(alcohol~Seat,data=ucdavis1)
```


Numerical summary shows the the median for back seat consumption is 3.5, front seat consumption 0.0 and middle seat consumption is 4.0,

## inferential description

```{r}
model1 <- aov(alcohol~Seat,data=davisdata)
summary.aov(model1)
```

The P value is 0.000116 is < 0.05 that mean that students in all the row did NOT consume the same amount of alcohol.

```{r}
plot(TukeyHSD(model1))
```

The model HSD shows that the people seated in the back row drink more  than the people sitting in the middle and front row. There is no evidence between alcohol consumption between  the middle and front row.



# Conclusion and Discussion


To answer the question if the amount of drinking varies weekly between front, middle, and back seats. we mus find the numerical value  and categorical mean of the front seats. the grafic shows that the P value is less than 0.05, this result in the rejection of the $H_0$: There is no difference per week between the different seating rows. There is no difference between middle and front seats.






 

```{r cars}
summary(cars)
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
