---
title: "Alcohol vs Seat choice"
author: "Yessica Garay"
date: "Spring 2024"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r include=FALSE}
require(tidyverse)
require(tigerstats)
davisdata <- read.csv(file="UCDavis.csv")
data(ucdavis1)
```
## Our Goal is to answer this question Is there a difference between the alcohol consumed between the row you choose to sit in??

# Introduction

Data are from the UCDavis.csv
Is the amount of alcohol consumed per week different for the different seating rows

$H_0$: There is no difference between the average number of drinks alcohol consumed per week base on the row they sit in.

$H_0$:  There is a difference between the average number of drinks alcohol consumed per week based on the row they sit in.

# Methods


Data from UC Davis: Seat is categorical, and alcohol is numerical so we use the Numerical~Cat helper file

# Description
## graphical description

```{r}
boxplot(Alcohol~Seat,data=davisdata)
```


## Now with ggplot - first select the basic data

```{r}
basicCN <- ggplot(davisdata,aes(y=alcohol,x=Seat))
```
## Now add in boxplot

```{r}
basicCN + geom_boxplot()
```
  
  
### get fancy  

```{r}
basicCN + geom_boxplot(notch=TRUE,outlier.color = "red") + stat_boxplot(geom ='errorbar') + labs(title="Fancy notch boxplot \n with 2 lines")
```

## Numerical Summarys 

## Inferential Tests

## Conclusions


